[dcpo_demsupport]

### 2020-07-22 paper/dcpo_demsupport.Rmd

>>>>

```{r dcpo-uncertainty}
# Preload function ----
vcovBK_se <- function(x) {
  vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

# Data input ----

load(here::here("data", "dcpo_input_update.rda"))
load(here::here("data", "dcpo_theta.rda"))

ls_year <- 1988:2017
ls_country <- dcpo_input$data$country %>% 
  unique

df_controls <- read_csv(here::here("data", "control_variables.csv"),
                        col_types = cols(
                          .default = col_double(),
                          Country = col_character(),
                          Cnt_code = col_character(),
                          ISO_code = col_character(),
                          Region_UN = col_character()))

first_year <- min(dcpo_input$data$year)

df_theta <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    as_tibble() %>% 
    rename_with(~ ls_country, .cols = starts_with("V")) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = ls_country,
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_dcpo_1k <- map(df_theta, function(aDataset) {
  plm(
    Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_UN, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset
  )
})

result_betas_dcpo_1k <- mitools::MIextract(result_dcpo_1k, fun = coef)
result_vars_dcpo_1k <- mitools::MIextract(result_dcpo_1k, fun = vcovBK_se)

summary(mitools::MIcombine(results = result_betas_dcpo_1k, 
                           variance = result_vars_dcpo_1k))

```
